---
output: pdf_document
title: "Supplemental material"
date: \today{}
geometry: margin=1in
header-includes:
   - \usepackage{dcolumn}
---


```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
load("../data/model_data.rda")
library(lme4)
library(stargazer)
library(xtable)
```

This document replicates the analysis in "Rice yield improvements
through plant breeding are offset by inherent yield declines over
time" (Espe et al, 2017) using classical/frequentist mixed-effects
models. The purpose of this document to verify the results are
consistent regardless of statistical method used (i.e., a "sanity
check"). As the tables below show, the estimates are indeed similar. As
such, please refer to the main manuscript for discussion of the model
estimates.

For each model, the structure is the same as used in the Bayesian
analysis (see main manuscript for details). The models were fit in R
using the 'lme4' package (Bates et al., 2015). The complete data,
code, and manuscript is available from
[https://github.com/mespe/rice_advances](https://github.com/mespe/rice_advances).

```{r, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
no_erosion = lmer(yield_kg ~ release_yr +
                      (1|id) + (1|year), data = mod_data)

stargazer(no_erosion, title = "Model excluding yield erosion.",
          ci = TRUE, ci.level = 0.90, float = TRUE,
          covariate.labels = c("Year of release", "Intercept"),
          dep.var.caption = "Response",
          dep.var.labels = "Yield ( kg/ha )",
          digits = 1, header = FALSE
          )

```

```{r, echo = FALSE, results = "asis"}
erosion = lmer(yield_kg ~ release_yr + yrs_in_trial +
                   (1|id) + (1|year), data = mod_data)

stargazer(erosion, title = "Model including yield erosion.",
          ci = TRUE, ci.level = 0.90, float = TRUE,
          covariate.labels = c("Year of release", "Yield erosion","Intercept"),
          dep.var.caption = "Response",
          dep.var.labels = "Yield ( kg/ha )",
          digits = 1, header = FALSE
          )
```

```{r, message = FALSE, warning = FALSE, results = "asis", echo = FALSE}
tt = anova(erosion, no_erosion)
row.names(tt) = c("Excluding yield erosion", "Including yield erosion")
print(xtable(tt,
             caption = "Model comparison"), comment = FALSE,
      caption.placement = "top")

```

